Descriptive analysis

### 2021-04-10 analysis/02_descriptive-analysis.Rmd
Minor renv changes

```{r load-libraries-data, message=FALSE, warning=FALSE}
library(tidyverse)
library(targets)
library(brms)
library(broom)
library(tidybayes)
library(sf)
library(scico)
library(scales)
library(patchwork)
library(ggtext)
library(here)

>>>>

```{r load-libraries-data, message=FALSE, warning=FALSE}
library(tidyverse)
library(targets)
library(brms)
library(broom)
library(tidybayes)
library(sf)
library(scico)
library(colorspace)
library(scales)
library(patchwork)
library(ggtext)
library(here)
